An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
I am confusion

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
As $\risk L_+$ is the $1$-homogeneous extension of $\risk L$, we observe $\risk L(x)_+ = \risk L(\bar x)$ for all $x \in \reals^\Y_+$.
Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.  But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
\end{proof}

@@

\lemmaX*
\begin{proof}
	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a finite set $\V^*\subseteq L(\R)$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
Hence, there is a finite set $\R^*$ such that $\V^* = L(\R^*)$. %, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$\raft{Edited and fleshed out}.
As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.

>>>>

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}\jessiet{So long as we're submitting to a single-blind venue, I'm fine with it.}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
As $\risk L_+$ is $1$-homogeneous, we observe $\risk L(x)_+ = \risk L_+(\|x\|_1 \bar x) = \|x\|_1 \risk L_+(\bar x) = \|x\|_1 \risk L(\bar x) \|x\|_1 = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$ for all $x \in \reals^\Y_+$, which is polyhedral as the pointwise min over a finite set of linear functions. 
\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.  But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
\end{proof}

@@

\lemmaX*
\begin{proof}
	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a finite set $\V^*\subseteq L(\R)$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
Hence, there is a finite set $\R^*$ such that $\V^* = L(\R^*)$. %, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$.
As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
